\textbf{plantecophys} : an R package for analysis and modelling of leaf gas exchange data

### 2014-12-03 manuscript/manuscript.Rnw
Added references and some text

% for bibtex
\bibliographystyle{plain}

@@

\title{Catchy article title}

@@

Time to cite some papers, some folks said so \cite{schenk_rooting_2002}, and some others as well \cite{mokany_critical_2006}.

@@

>>>>

% for bibtex
\usepackage{authordate1-4}
\bibliographystyle{authordate1}

@@

\title{\textbf{plantecophys} : an R package for analysis and modelling of leaf gas exchange data}

@@

The Farquhar model of photosynthesis is widely used \cite{Farquhar1980}. Various methods exist to fit the model to data. We have implemented \texttt{fitaci}, which fits the model in two different ways. The function \texttt{Aci} simulates the A-Ci curve.

The intersection of the supply and demand curves of photosynthesis gives the operating intercellular CO$_2$ concentration 
\cite{Farquhar1982}. This is solved by the \texttt{Photosyn} function.

Implementation of several stomatal conductance models, including \cite{ballberry1987,leuning1995,medlyn2011}.

We have used the code in several of our papers, including \cite{medlyn2011,duursma2013,duursma2014}

Full numerical optimizatin of the Cowan-Farquhar hypothesis. We have used this code in \cite{medlyn2011}, and is very similar to that used by \cite{buckley2014}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{figure2.pdf}
    \caption{The intersection of the supply and demand curves of photosynthesis as solved by \texttt{Photosyn}.}
    \label{fig:figure1}
\end{figure}
